\documentclass[12pt]{article}
\usepackage[ansinew]{inputenc} % ASCII (Western CP)
\usepackage{graphicx}
\usepackage{color}
\usepackage[colorlinks]{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}

\title{Probability and Computing - HW1}
\author{Pang Liang\\ Student No. 201418013229033}

\begin{document}
\maketitle

\section{Problem1}
Deduce the expected run time of Quick-Sort, using conditional expectation.\\

Note that $C(N)$ be an compare times of length $N$ list. Then $C(N) = C(Y-1)+C(N-Y)+N, p=i$. Then we apply expectation of both side.
\begin{equation}
    \begin{split}
    E(C(N)) &= \sum_Y E(C(Y-1) | Y=i) + \sum_Y E(C(N-Y) | Y=i) + N-1 \\
            &= \frac{1}{N} \sum_Y E(C(i-1)) + E(C(N-i)) + N-1 \\
            &= \frac{2}{N} \sum_Y E(C(i-1)) + N-1 \\
    \end{split}
\end{equation}
We are guessing that $E(C(N))\le ci \ln i$, so
\begin{equation}
    \begin{split}
    E(C(N)) &\le (N-1)+\frac{2}{N} \sum_{i=1}^{N}(c i \ln i) \\
            &\le (N-1)+\frac{2}{N} \int_{1}^{N} (c x \ln x) dx \\
            &\le (N-1)+\frac{2}{N}((c/2)N^2\ln N - cN^2/4+c/4)\\
            &\le cN \ln N, for c=2
    \end{split}
\end{equation}
$E(C(N)) \le 2N\ln N$.

\section{Problem2}
Why does the probability that the second door hides a car changes after Monty Hall opens the third door? An intuitive interpretation is preferred.\\

Because the Monty Hall knew the result of the door. In term of the information theory, Monty Hall gave some information to the player. So if he change his choose will increase the probability of choosing a car.

Firstly, random choose a door has $1/3$ probability. After open a door, the door remained has probability of $2/3$ is bigger then the previous $1/3$.

\section{Problem3}
The proof of Jensen's Inequality in the text book assumes that the convex function $f$ is twice differentiable. Present a convex function that is not differentiable, and show that Jensen's Inequality holds even if the convex function is not differentiable. Only discrete probability is considered.\\

Consider the function of $f(X) = |X|$, which is a convex function but is not differentiable (at $X=0$ is undefined).

\begin{equation}
    \begin{split}
    E[f(X)] &= \sum_{X\in \Omega} f(X) Pr(X) \\
            &= \sum_{X>=0} X Pr(X) + \sum_{X<0} (-X) Pr(X)
    \end{split}
\end{equation}
\begin{equation}
    \begin{split}
    f[E(X)] &= f(\sum_{X>=0} X Pr(X) + \sum_{X<0} X Pr(X))\\
            &= |\sum_{X>=0} X Pr(X) + \sum_{X<0} X Pr(X)| \\
            &\le |\sum_{X>=0} X Pr(X)| + |\sum_{X<0} X Pr(X)| \\
            &= \sum_{X>=0} X Pr(X) + \sum_{X<0} (-X) Pr(X) \\
            &= E[f(X)]
    \end{split}
\end{equation}
So $E[f(X)] \ge f(E[X])$.

\section{Problem4}
Do Bernoulli experiment for 20 trials, using a new 1-Yuan coin. Send the result to \url{advanced\_algorithm@163.com} in a string $s_1s_2 \cdots s_i \cdots s_{20}$, where $s_i$ is 1 if the $i^{th}$ trial gets Head, and otherwise is 0.\\

0010000110 1111100011
\end{document}
