\documentclass[12pt]{article}
\usepackage[ansinew]{inputenc} % ASCII (Western CP)
\usepackage{graphicx}
\usepackage{color}
\usepackage[colorlinks]{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=2.5cm}

\title{Probability and Computing - HW6}
\author{Pang Liang\\ Student No. 201418013229033}

\begin{document}
\maketitle

\section{Problem1}
Given an n-vertex undirected graph $G = (V, E)$, consider the following method of generating an independent set. Given a permutation $\sigma$ of the vertices, define a subset $S(\sigma)$ of the vertices as follows: for each vertex $i, i \in S(\sigma)$ if and only if no neighbor $j$ of $i$ precedes $i$ in the permutation $\sigma$.

\begin{itemize}
\item Show that each $S(\sigma)$ is an independent set in $G$.
\item Suggest a natural randomized algorithm to produce $\sigma$ for which you can show that the expected cardinality of $S(\sigma)$ is $\sum_{i=1}^{n} \frac{1}{d_i+1}$, where $d_i$ denotes the degree of vertex $i$.
\item De-randomizing the above algorithm.
\end{itemize}

Solution:\\
\begin{itemize}
\item
According to the algorithm describe above, we denote the permutation $\sigma$ as $\sigma = {v_1, v_2, \dots, v_i, \dots, v_n}$ where $n$ is the number of vertex. And $S(\sigma)={d_1, d_2, \dots, d_k}$, where $k$ is the size of $S(\sigma)$. Obviously, $d_1 = v_1 \in S(\sigma)$ as the first element. Let's look at the $d_i$ which belongs to $S(\sigma)$. There's no connection with the $d_j$ where $j<i$, because no neighbor of it precedes before. And any $d_j$ where $j>i$ has no connection with $d_i$ for the same reason. So the vertices in $S(\sigma)$ is an independence set in $G$.

\item
With the natural randomized algorithm to produce $\sigma$. The expectation of vertex $v_i$ in the subset $S(\sigma)$ is $E(v_i) = \frac{1}{d_i+1}$, for the reason of that $v_i$ need occur first within its $d_i$ neighbors and itself, so the probability of that is $\frac{1}{d_i+1}$.\\
So consider all of $n$ vertices $E(S(\sigma)) = \sum_{i=1}^{n} \frac{1}{d_i+1}$.

\item
Define 3 kind of vertices set: Unused, $S(\sigma)$, Used. First we random select a vertex in Unused set. Then add this vertex's neighbors and itself into Used set, add itself into $S(\sigma)$, and delete this vertex's neighbors and itself in Unused set. Repeat this step, until the Unused set is empty.\\
In order to change this algorithm to a de-randomizing one, we change the first step (random select a vertex) to a definite step. We choose the one has the largest degree.

\end{itemize}

\section{Problem2}
Prove that, for every integer $n$, there exists a way to 2-color the edges of $K_x$ so that there is no monochromatic clique of size $k$ when $x = n - ({}_k^n) 2^{1-({}_2^k)}$. Note that $K_x$ stands for the x-vertex complete graph. (Hint, start by 2-coloring the edges of $K_n$ and fix things up.)

Solution:\\
In $K_n$ graph chose a k-cliques from $({}_k^n)$ k-cliques in $K_n$. Let $X_i$ be an random variable, such that $X_i=1$ if clique $i$ is monochromatic and 0 otherwise. Further let $X=\sum X_i$.\\
\begin{equation}
E[X] = \sum E[X_i] = ({}_k^n) 2^{-({}_2^k)+1}
\end{equation}

Then we remove a vertex from each monochromatic k-clique. Then the residual graph is a complete graph without monochromatic k-cliques. The expectation of number of vertices in the residual graph is
\begin{equation}
    n-E[X] = n - ({}_k^n) 2^{-({}_2^k)+1} = x
\end{equation}

So there is a 2-coloring of $K_n$ where removing a vertex from each monochromatic k-clique results in a $K_y$, $y\ge x$ that has no monochromatic k-clique. If $K_y$ does not have a monochromatic $K_k$, because $y \ge x$ $K_x$ does not have too.

\section{Problem3}
Prove the following claims.
\begin{itemize}
\item For every integer $n$, there exists a coloring of the edges of the complete graph $K_n$ by two colors so that the total number of monochromatic copies of $K_4$ is at most $({}_4^n) 2^{-5}$.
\item Give a randomized algorithm for finding a coloring with at most $({}_4^n) 2^{-5}$ monochromatic copies of $K_4$ that runs in expected time polynomial in $n$.
\item Show how to construct such a coloring deterministically in polynomial time using the method of conditional expectations.
\end{itemize}

Solution:\\
\begin{itemize}
\item
First we consider random 4 vertices in n-vertices graph. Once one of edges is colored, then the remain $({}_2^4)-1 = 5$ edges have the probability $Pr(A_i) = 2^{-5}$ to color to the same color. Where $A_i$ denote the event that clique $i$ is monochromatic in $({}_4^n)$ cliques. Also we define that if clique $i$ is monochromatic then random variable $A_i=1$, otherwise $A_i=0$. So $E(A_i) = 2^{-5}$.\\
In order to calculate $E(\sum A_i)$ we yields:
\begin{equation}
    E(\sum A_i) = ({}_4^n)2^{-5}
\end{equation}
Using the Lemma 6.2 we have $Pr(\sum A_i \le ({}_4^n)2^{-5})>0 $
So there exist one 2-coloring that has at most $({}_4^n)2^{-5}$ $K_4$ are monochromatic.

\item
Color the edge independently and uniformly. Denote $X = \sum A_i$. Let $p = Pr(X \le ({}_4^n)2^{-5}$. Then we have
\begin{equation}
    \begin{split}
    ({}_4^n)2^{-5} &= E[X] \\
    &= \sum_{i \le ({}_4^n)2^{-5}} i Pr(X=i) + \sum_{i \ge ({}_4^n)2^{-5}+1} i Pr(X=i) \\
    &\ge p + (1-p) ({}_4^n)2^{-5}+1 \\
    \end{split}
\end{equation}
So we have
\begin{equation}
    \frac{1}{p} \le ({}_4^n)2^{-5}
\end{equation}
Thus, the expected number of samples is at most $({}_4^n)2^{-5}$. Testing to see if $X \le ({}_4^n)2^{-5}$ can be done in $O(n^4)$ time. So the algorithm can be done in polynomial time.
\item
Assign values to variables deterministically, one at a time, in an arbitrary order
$x_1, x_2, \dots , x_n$. Suppose that we have assigned the first k edge. Let $y_1, y_2, \dots , y_k$
be the corresponding assigned values. We compute the two quantities,
\begin{equation}
    \begin{split}
    E[X | x_1 = y_1, x_2 = y_2, . . . , x_k = y_k, x_{k+1} = color_1 ]\\
    E[X | x_1 = y_1, x_2 = y_2, . . . , x_k = y_k, x_{k+1} = color_2 ]\\
    \end{split}
\end{equation}
and then choose the setting with larger expectation.
\end{itemize}
\section{Problem4}
Do Bernoulli experiment for 20 trials, using a new 1-Yuan coin. Record the result in a
string $s_1s_2 \cdots s_i \cdots s_{20}$, where $s_i$ is 1 if the $i^{th}$ trial gets Head, and otherwise is 0.

0100110100 0100111011

\end{document}
